---
title: "Shiny_R"
author: "Haochen_Li"
date: "2024-11-16"
output: html_document
runtime: shiny
---

# Q: What is the difference between Hadley_1 and Hadley_2?

## Hadley_1

```{r setup, include=FALSE}
library(shiny)
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)


server <- function(input, output, session) {
  output$summary <- renderPrint({
    dataset <- get(input$dataset, "package:datasets")
    summary(dataset)
  })
  
  output$table <- renderTable({
    dataset <- get(input$dataset, "package:datasets")
    dataset
  })
}

shinyApp(ui, server)
```

## Hadley_2

```{r}
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)

server <- function(input, output, session) {
  # Create a reactive expression
  dataset <- reactive({
    get(input$dataset, "package:datasets")
  })

  output$summary <- renderPrint({
    # Use a reactive expression by calling it like a function
    summary(dataset())
  })
  
  output$table <- renderTable({
    dataset()
  })
}
shinyApp(ui, server)

```

### In Hadley_1, the dataset is retrieved using get() directly inside each output 
rendering function (renderPrint and renderTable), resulting in repetitive calls 
every time the outputs are updated. This approach can lead to inefficiency and 
redundant computations, making it harder to manage, especially when multiple
outputs depend on the same dataset. 

### In contrast, Hadley_2 uses a reactive expression to fetch the dataset once 
when the input changes, storing it as a reusable object that can be accessed 
by calling the reactive expression as dataset(). This method improves efficiency,
reduces redundancy, and simplifies the code by centralizing dataset retrieval 
logic, making it better suited for complex applications.


# 2.3.5

# Which of textOutput() and verbatimTextOutput() should each of the following render
# functions be paired with?

renderPrint(summary(mtcars)): verbatimTextOutput()

renderPrint() is used for displaying textual outputs such as summaries 
or test results with formatting that preserves whitespace and layout.

renderText("Good morning!"): textOutput()

Reason: renderText() generates simple plain text output suitable for use with 
textOutput().

renderPrint(t.test(1:5, 2:6)): verbatimTextOutput()

The output of a statistical test is a formatted text object, best displayed with 
preserved formatting using verbatimTextOutput().

renderText(str(lm(mpg ~ wt, data = mtcars))): textOutput()

Although str() gives detailed information, when combined with renderText(), it 
is treated as simple text output, best displayed with textOutput().


## 2:

```{r}
library(shiny)

ui <- fluidPage(
  plotOutput("scatterplot", height = "300px", width = "700px")
)

server <- function(input, output, session) {
  output$scatterplot <- renderPlot({
    plot(runif(5), runif(5), main = "Scatterplot of Random Numbers")
  }, alt = "A scatterplot of five random numbers.")
}

shinyApp(ui, server)

```

## 3:

```{r}
library(shiny)
library(DT)

ui <- fluidPage(
  DTOutput("table")
)

server <- function(input, output, session) {
  output$table <- renderDT(
    mtcars,
    options = list(
      pageLength = 5,
      ordering = FALSE,
      searching = FALSE
    )
  )
}

shinyApp(ui, server)
```

# 3.3.6

## 1.

Given:

```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
```

```{r}
#Replace input$greeting with output$greeting and ensure the paste0() function references input$name
server1 <- function(input, output, server) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}

# Move the paste0() logic inside the renderText() function
server2 <- function(input, output, server) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}

#Wrap the paste0() logic in renderText()
server3 <- function(input, output, server) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
```

## 2:

## Reactive Graph 1

```{r}
library(DiagrammeR)

DiagrammeR::grViz("
digraph ReactiveGraph1 {
  rankdir=TB;
  node [shape=box, style=filled, color=lightblue];
  
  a [label='input$a'];
  b [label='input$b'];
  d [label='input$d'];
  c [label='reactive(c)\\n(c <- input$a + input$b)'];
  e [label='reactive(e)\\n(e <- c() + input$d)'];
  f [label='output$f\\n(renderText(e()))'];
  
  a -> c;
  b -> c;
  c -> e;
  d -> e;
  e -> f;
}
")

```


## Reactive Graph 2

```{r}
DiagrammeR::grViz("
digraph ReactiveGraph2 {
  rankdir=TB;
  node [shape=box, style=filled, color=lightblue];
  
  x1 [label='input$x1'];
  x2 [label='input$x2'];
  x3 [label='input$x3'];
  y1 [label='input$y1'];
  y2 [label='input$y2'];
  x [label='reactive(x)\\n(x <- input$x1 + input$x2 + input$x3)'];
  y [label='reactive(y)\\n(y <- input$y1 + input$y2)'];
  z [label='output$z\\n(renderText(x() / y()))'];
  
  x1 -> x;
  x2 -> x;
  x3 -> x;
  y1 -> y;
  y2 -> y;
  x -> z;
  y -> z;
}
")

```


## Reactive Graph 3

```{r}
DiagrammeR::grViz("
digraph ReactiveGraph3 {
  rankdir=TB;
  node [shape=box, style=filled, color=lightblue];
  
  a_input [label='input$a'];
  b_input [label='input$b'];
  c_input [label='input$c'];
  d_input [label='input$d'];
  a [label='reactive(a)\\n(a <- input$a * 10)'];
  b [label='reactive(b)\\n(b <- a() + input$b)'];
  c [label='reactive(c)\\n(c <- b() / input$c)'];
  d [label='reactive(d)\\n(d <- c() + input$d)'];
  output [label='output'];

  a_input -> a;
  a -> b;
  b_input -> b;
  b -> c;
  c_input -> c;
  c -> d;
  d_input -> d;
}
")

```


## 3: Why will this code fail?

The code fails because var and range are names of base R functions, and using 
them for reactive expressions overrides their default behavior, causing conflicts.
These names are bad for reactives because they can unintentionally break the 
functionality of the original functions, making debugging difficult. To avoid 
such issues, use unique and descriptive names for reactive expressions, such as
selected_var or computed_range.


# 4.8

## 1

### Prototype App

```{r}
DiagrammeR::grViz("
digraph prototype {
  rankdir=LR;
  node [shape=box, style=filled, color=lightblue];
  code [label='input$code'];
  selected [label='selected()'];
  summary [label='summary()'];
  diag [label='output$diag'];
  body_part [label='output$body_part'];
  location [label='output$location'];
  age_sex [label='output$age_sex'];

  code -> selected;
  selected -> diag;
  selected -> body_part;
  selected -> location;
  selected -> summary;
  summary -> age_sex;
}
")

```

### Rate vs. Count App


```{r}
DiagrammeR::grViz("
digraph rate_vs_count {
  rankdir=LR;
  node [shape=box, style=filled, color=lightblue];
  code [label='input$code'];
  y [label='input$y'];
  selected [label='selected()'];
  summary [label='summary()'];
  diag [label='output$diag'];
  body_part [label='output$body_part'];
  location [label='output$location'];
  age_sex [label='output$age_sex'];

  code -> selected;
  selected -> diag;
  selected -> body_part;
  selected -> location;
  selected -> summary;
  y -> summary;
  summary -> age_sex;
}
")

```

### Narrative App

```{r}
DiagrammeR::grViz("
digraph narrative {
  rankdir=LR;
  node [shape=box, style=filled, color=lightblue];
  code [label='input$code'];
  y [label='input$y'];
  story [label='input$story'];
  selected [label='selected()'];
  summary [label='summary()'];
  diag [label='output$diag'];
  body_part [label='output$body_part'];
  location [label='output$location'];
  age_sex [label='output$age_sex'];
  narrative [label='output$narrative'];

  code -> selected;
  selected -> diag;
  selected -> body_part;
  selected -> location;
  selected -> summary;
  selected -> narrative;
  y -> summary;
  summary -> age_sex;
  story -> narrative;
}
")

```

## 2:

Applying fct_lump() before fct_infreq(), the lumped levels
are not considered in frequency reordering, which may give unexpected results. 
Conversely, applying fct_infreq() first ensures proper reordering before lumping.

## 3:

```{r}
# ui <- fluidPage(
#   fluidRow(
#     column(8,
#            selectInput("code", "Product",
#                        choices = setNames(products$prod_code, products$title),
#                        width = "100%")
#     ),
#     column(2, selectInput("y", "Y axis", c("rate", "count"))),
#     # Add a numeric input for the number of rows
#     column(2, numericInput("num_rows", "Number of Rows", value = 5, min = 1, max = 10))
#   ),
#   fluidRow(
#     column(4, tableOutput("diag")),
#     column(4, tableOutput("body_part")),
#     column(4, tableOutput("location"))
#   ),
#   fluidRow(
#     column(12, plotOutput("age_sex"))
#   ),
#   fluidRow(
#     column(2, actionButton("story", "Tell me a story")),
#     column(10, textOutput("narrative"))
#   )
# )

```

## 4:

Add actionButton elements for navigation in the fluidRow where the narrative is displayed:


```{r}
# fluidRow(
#   column(2, actionButton("prev", "Previous")),
#   column(2, actionButton("next", "Next")),
#   column(8, textOutput("narrative"))
# )
```

To allow users to navigate narratives systematically, we add two buttons: 
prev_story and next_story. When clicked, these buttons update the current position 
in the narrative list. To make the navigation circular, we use the modulus operator
(%%) to ensure the index always stays within the range of available stories.

Key Steps:
Add Buttons in the UI:

prev_story: For moving to the previous story.
next_story: For moving to the next story.
Track the Current Story:

Use a reactive value, story, to store the current story index.

When "Next story" is clicked, increment the index using story((story() %% max_no_stories()) + 1).
When "Previous story" is clicked, decrement the index, ensuring it wraps around using story(((story() - 2) %% max_no_stories()) + 1).
Reset on Product Change:

Reset the story index to the first narrative when the product (input$code) changes.
Render the Narrative:

Use renderText to display the story corresponding to the current index in the list of narratives.
Highlights:
Circular Navigation:

Clicking "Next" from the last story wraps to the first.
Clicking "Previous" from the first story wraps to the last.



```{r}
#Navigation
# observeEvent(input$next_story, {
#   story((story() %% max_no_stories()) + 1)
# })
```

```{r}
# observeEvent(input$prev_story, {
#   story(((story() - 2) %% max_no_stories()) + 1)
# })
```

```{r}
# output$narrative <- renderText({
#   selected()$narrative[story()]
# })
```























